Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-06-23 Latex/journal_v1/V4/pr.tex
add algorithm

& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{c17}  \\
& \sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\

@@

\eqref{c17} and \eqref{c18} guarantee that O-RU and PRB is associated to the UE, respectively.

@@

the numerator and the denominator will be both negative. Using \eqref{c16-2},
in numerator, $\alpha_s \geq 0$, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$ and 
$(R_{u(s,i)}-\lambda_{u(s,i)})T_{max}^s \leq 1$. So the numerator is negative.
In denominator, it can be said approximately that $(T_{max}^s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \leq 0 $, since, $(R_{u(s,i)}-\lambda_{u(s,i)}) \leq 1/T_{max}^s$.

@@

In order to make \eqref{problem} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint 
\eqref{c15} is changed to
 $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
The combination of equations \eqref{c13} and \eqref{c15} leads to the following equation
\begin{equation}
\begin{split}
\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
P_r &\leq  \zeta_{r}.\\
\end{split}
\end{equation} 
Moreover, the combination of equations \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
\begin{equation}\label{RConstr}
\begin{split}
\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{max}, \lambda_{u_{(s,i)}}, \varpi_{u(s,i)} \}, \\
\mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
\end{split}
\end{equation}
Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.

@@

\subsection{Sub-Problem 2}

@@

Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
The problem can be solved by two different method. 
Next we introduce the first method which is a greedy algorithm.
\begin{enumerate}
\item \textit{Greedy Algorithm:}
The problem can be reformulated as follow
\begin{subequations}\label{problem2}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}  g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
\text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r
 \label{p11} \\
& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{p12}\\
 & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{p13}  
\end{alignat}
\end{subequations}
Where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
and $\mathfrak{t}_r = \zeta_r- \sigma_r$
Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
To simplicated  and reformulated to the multiple knapsack problem suppose that each UE in each service is associated to only one O-RU. Therefore, constraint \eqref{p12} is restricted to equality
($\sum_{r=1}^R g^r_{u(s,i)} = 1 $). By changing this constraint,
the problem \eqref{problem2} convert to an NP-complete 0-1 multiple knapsack problem.  
We solve this problem using GAAOU which is a greedy algorithm \eqref{alg1} as follow \cite{akccay2007greedy,lee2018dynamic}.
Firstly, we set all variables $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$. 
Then we define ${RU}_{resid} = \mathcal{R} $ and $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
as a set of O-RUs and value of each O-RU, respectively.
Afterward, we assign the O-RU that provides the highest achievable rate for each UE on the condition that 
it does not exceed the value of each O-RU (that is a function of maximum power and capacity of O-RU).
If it exceeds the value of O-RU, then O-RU with the next highest achievable rate is selected. 
Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ 
The complexity of this algorithm is about $O(N\times \mathfrak{N})$
\begin{algorithm}
\caption{Greedy Algorithm for Assignment of O-RU to UEs (GAAOU)}\label{alg1}
\begin{algorithmic}[1]
\State Set $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$.\label{31}
\State Set ${RU}_{resid} = \mathcal{R} $ and $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
\For {$s \gets 1$ to $S$}\label{33}
\For {$i \gets 1$ to $U_s$}
\For {$r \gets 1$ to $R$}
\State Acquire $\mathfrak{G}_r = \bar{\mathcal{R}}^r_{u_{(s,k)}}$
\EndFor
\State \textbf{end for}
\State Obtain $r = \text{argmax}_r \mathfrak{G}_r$
\While{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
\If{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
\State Set $g^r_{u(s,i)} = 1$ and $\mathfrak{C}_r = \mathfrak{C}_r - \psi_{r,u(s,i)}$
\Else
\State  ${RU}_{resid} = \mathcal{R} \setminus \{r\} $
\EndIf
\State \textbf{end if}
\EndWhile
\State \textbf{end while}
\EndFor
\State \textbf{end for}
\EndFor
\State \textbf{end for} \label{34}
\end{algorithmic}
\end{algorithm}
\item\textit{Lagrangian Function:} The second method to solve the O-RU assignment is to relax $\boldsymbol{G}$ between zero and one and solve the problem using Lagrangian function.

\end{enumerate} 
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}

>>>>

& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\
& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18-1} \\
& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\

@@

\eqref{c17} and \eqref{c18-1} guarantee that O-RU and PRB is associated to the UE, respectively.
Also, \eqref{c18} ensure that each PRB can not be assigned to more than one UE associated to the same O-RU.

@@

the numerator and the denominator will both have same sign. Using \eqref{c16-2},
in numerator, $\alpha_s \geq 0$, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$ and to simplify the problem, assume 
$(R_{u(s,i)}-\lambda_{u(s,i)})T_{max}^s \geq 1$ since the order of $T_{max}^s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T_{max}^s$.
Therefore, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T_{max}^s$.
So the numerator is positive.
In denominator, it can be said approximately that $(T_{max}^s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since, $(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T_{max}^s$ as mentioned above.

@@

In order to make \eqref{problem} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint 
\eqref{c15} is changed to
 $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
The combination of equations \eqref{c13} and \eqref{c15} leads to the following equation
\begin{equation}
\begin{split}
\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
P_r &\leq  \zeta_{r}.\\
\end{split}
\end{equation} 
Moreover, the combination of equations \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
\begin{equation}\label{RConstr}
\begin{split}
\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{max}, \lambda_{u_{(s,i)}}+1/T^s_{max}, \varpi_{u(s,i)} \}, \\
\mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
\end{split}
\end{equation}
Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.

@@

\subsection{Sub-Problem 2}\label{sub2}

@@

Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
Next we introduce the  method which is a greedy algorithm.

\textit{Greedy Algorithm:}
The problem can be reformulated as follow
\begin{subequations}\label{problem2}
\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}  g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
\text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r
 \label{p11} \\
& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{p12}\\
 & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{p13}  
Where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
and $\mathfrak{t}_r = \zeta_r- \sigma_r$
Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.  
We solve this problem using GAAOU which is a greedy algorithm \eqref{alg1} as follow \cite{akccay2007greedy,lee2018dynamic}.
Firstly, we set all variables $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$. 
Then we define ${RU}_{resid} = \mathcal{R} $ and $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
as a set of O-RUs and value of each O-RU, respectively.
Afterward, we assign the O-RU that provides the highest achievable rate for each UE on the condition that 
it does not exceed the value of each O-RU (that is a function of maximum power and capacity of O-RU).
If it exceeds the value of O-RU, then O-RU with the next highest achievable rate is selected. 
Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ 
The complexity of this algorithm is about $O(N\times \mathfrak{N})$
\begin{algorithm}
\caption{Greedy Algorithm for Assignment of O-RU to UEs (GAAOU)}\label{alg1}
\begin{algorithmic}[1]
\State Set $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$.\label{31}
\State Set ${RU}_{resid} = \mathcal{R} $ and $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
\For {$s \gets 1$ to $S$}\label{33}
\For {$i \gets 1$ to $U_s$}
\For {$r \gets 1$ to $R$}
\State Acquire $\mathfrak{G}_r = \bar{\mathcal{R}}^r_{u_{(s,k)}}$
\EndFor
\State \textbf{end for}
\State Obtain $r = \text{argmax}_r \mathfrak{G}_r$
\While{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
\If{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
\State Set $g^r_{u(s,i)} = 1$ and $\mathfrak{C}_r = \mathfrak{C}_r - \psi_{r,u(s,i)}$
\Else
\State  ${RU}_{resid} = \mathcal{R} \setminus \{r\} $
\EndIf
\State \textbf{end if}
\EndWhile
\State \textbf{end while}
\EndFor
\State \textbf{end for}
\EndFor
\State \textbf{end for} \label{34}
\end{algorithmic}
\end{algorithm}
\subsection{Iterative Proposed Algorithm}
In \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
Here, the iterative algorithm for the whole problem is demonstrated.
Firstly, we fixed $\boldsymbol{G}$, then $\boldsymbol{P}$ and $\boldsymbol{E}$ is achieved using Lagrangian method.  
Afterward, $\boldsymbol{G}$ is updated using GAAOU algorithm. This process is repeated until it converges. 
The whole algorithm is depicted as follow (Algorithm \eqref{alg2}).
 \begin{algorithm}
\caption{Iterative Algorithm for Power Allocation, PRB, VNF and O-RU Association (IAPPVO)}\label{alg2}
\begin{algorithmic}[1]
\State  Set the maximum number of iterations ${Iter}_{max}$, convergence condition $\epsilon > 0$ \label{a21}
\State  Assign Users to O-RU randomly (Initialize $\boldsymbol{G}$) \label{a22}
\For {$i \gets 1$ to $Iter_{max}$}\label{33}
\State Acquire $\boldsymbol{P}^{(i)}$, $\boldsymbol{E}^{(i)}$ and $\boldsymbol{M}^{(i)}$ using Lagrangian function and sub-gradient method based on \eqref{sub1}
\State Update $\boldsymbol{G}^{(i)}$   based on algorithm GAAOU \eqref{alg1} in  \eqref{sub2}
\If {the algorithm converged with the tolerence of $\epsilon$}
\State Break
\Else 
\State Continue the algorithm  
\EndIf
\State \textbf{end if}
\EndFor
\State \textbf{end for} \label{34}
\end{algorithmic}
\end{algorithm}
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}
